Analysis

### 2024-03-25 production/prod_analysis-fix-t5.Rmd
render paper

omit <- "(education)|(ess)"
texreg::htmlreg(list(educ0, educ1, educ2, educ3, educ4, educ5, educ6),
                custom.note = "*** p < 0.001; ** p < 0.01; * p < 0.05. <br>
Note: Model 3 to 7 are controlled by educational level, and subjective social status with no significant effects.", 
                omit.coef = omit,
                custom.coef.names = c("Intercept",
                                      "Wave 2017 <br> <i>(Ref. Wave 2016)</i>",
                                      "Wave 2018",
                                      "Wave 2019",
                                      "Wave 2022",
                                      "Wave",
                                      "Wave^2",
                                      "Quintile 2 <br> <i>(Ref. Quintile 1)</i>",
                                      "Quintile 3",
                                      "Quintile 4",
                                      "Quintile 5",
                                      "Quintile NA",
                                      "Age 30-49 <br> <i>(Ref. 18-29)</i>",
                                      "Age 50-64",
                                      "Age 65 o más",
                                      "Gender <br> <i>(Ref. Male)</i>",
                                      "Pol. pos: Center <br> <i>(Ref. Left)</i>",
                                      "Pol. pos: Right",
                                      "Pol. pos: Does not identify",
                                      "Inequality perception",
                                      "Merit: Talent",
                                      "Merit: Effort" ),
                custom.gof.names = c("AIC",
                                     "BIC",
                                     "Log Likelihood",
                                     "Num. obs.",
                                     "Num. groups: Individuals",
                                     "Var: Individuals (Intercept)",
                                     "Var: Residual"),
                file = "output/tables/table1-individuales-pond-v2.html")
          #omit.coef = omit

@@

# Hipotesis
#h1b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort"
h2b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+merit_effort+merit_effort*ola+merit_effort*ola_2"
h3b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+merit_talent+merit_talent*ola+merit_talent*ola_2"
h4b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+des_perc*ola+des_perc*ola_2"
#h5b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort+ola_2*pos_id"
#h6b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort+ola_2*sexo"
#h7b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort+ola_2*quintil1"
#h8b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort+ola_2*edad"

# A. justification educational inequality
#educ1 <- lmer(formula(paste0("just_educ~",h1b,"+(ola+ola_2|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ2 <- lmer(formula(paste0("just_educ~",h2b,"+(ola+ola_2+merit_effort|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ3 <- lmer(formula(paste0("just_educ~",h3b,"+(ola+ola_2+merit_talent|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ4 <- lmer(formula(paste0("just_educ~",h4b,"+(ola+ola_2+des_perc|idencuesta)")),data = df_study1, weights = ponderador_long_total)
#educ5 <- lmer(formula(paste0("just_educ~",h5b,"+(ola+ola_2|idencuesta)")),data = df_study1, weights = ponderador_long_total)
#educ6 <- lmer(formula(paste0("just_educ~",h6b,"+(ola+ola_2|idencuesta)")),data = df_study1, weights = ponderador_long_total)
#educ7 <- lmer(formula(paste0("just_educ~",h7b,"+(ola+ola_2|idencuesta)")),data = df_study1, weights = ponderador_long_total)
#educ8 <- lmer(formula(paste0("just_educ~",h8b,"+(ola+ola_2|idencuesta)")),data = df_study1, weights = ponderador_long_total)

# table 3: interacciones
omit <- "(education)|(ess)|(quintil1)|(edad)|(sexo)|(pos_id)"
texreg::htmlreg(list(educ2,educ3,educ4),
                custom.note = "*** p < 0.001; ** p < 0.01; * p < 0.05. <br>
Note: All the models are controlled by educational level, income quintile, subjective social status, age, gender and political position",
                omit.coef = omit,
                custom.coef.names = c("Intercept",
                                      "Wave",
                                      "Wave^2",
                                      "Merit: Effort",
                                      "Wave * Merit: Effort",
                                      "Wave^2 * Merit: Effort",
                                      "Merit: Talent",
                                      "Wave * Merit: Talent",
                                      "Wave^2 * Merit: Talent",
                                      "Inequality perception",
                                      "Wave * Inequality perception",
                                      "Wave^2 * Inequality perception"
                                      ),
                custom.gof.names = c("AIC", "BIC", "Log Likelihood",
                                     "Num. obs.",
                                     "Num. groups: Individuals",
                                     "Var: Individuals (Intercept)",
                                     "Var: Individuals Wave",
                                     "Var: Individuals Wave^2",
                                     "Var: Individuals Merit: Effort",
                                     "Cov: Individuals (Intercept) Wave",
                                     "Cov: Individuals (Intercept) Wave^2",
                                     "Cov: Individuals (Intercept) Merit: Effort",
                                     "Cov: Individuals Wave Wave^2",
                                     "Cov: Individuals Wave Merit: Effort",
                                     "Cov: Individuals Wave^2 Merit: Effort",
                                     "Var: Residual",
                                     "Var: Individuals Merit: Talent",
                                     "Cov: Individuals (Intercept) Merit: Talent",
                                     "Cov: Individuals Wave Merit: Talent",
                                     "Cov: Individuals Wave^2 Merit: Talent",
                                     "Var: Individuals Inequality perception",
                                     "Cov: Individuals (Intercept) Inequality perception",
                                     "Cov: Individuals Wave Inequality perception",
                                     "Cov: Individuals Wave^2 Inequality perception"
                                     ),
                file = "output/tables/table3-interac_pond.html")
          #omit.coef = omit

>>>>

omit <- "(education)|(ess)"
texreg::htmlreg(list(educ0, educ1, educ3, educ4, educ5, educ6),
                custom.note = "*** p < 0.001; ** p < 0.01; * p < 0.05. <br>
Note: Model 3 to 6 are controlled by educational level, and subjective social status with no significant effects.", 
                omit.coef = omit,
                custom.coef.names = c("Intercept",
                                      "Wave 2017 <br> <i>(Ref. Wave 2016)</i>",
                                      "Wave 2018",
                                      "Wave 2019",
                                      "Wave 2022",
                                      "Wave",
                                      "Wave^2",
#                                      "High School <br> <i>(Ref. Primary)</i>",
#                                      "Technical",
#                                      "Universitary",
                                      "Quintile 2 <br> <i>(Ref. Quintile 1)</i>",
                                      "Quintile 3",
                                      "Quintile 4",
                                      "Quintile 5",
                                      "Quintile NA",
#                                      "Subjective Social Status",
                                      "Age 30-49 <br> <i>(Ref. 18-29)</i>",
                                      "Age 50-64",
                                      "Age 65 o más",
                                      "Gender <br> <i>(Ref. Male)</i>",
                                      "Pol. pos: Center <br> <i>(Ref. Left)</i>",
                                      "Pol. pos: Right",
                                      "Pol. pos: Does not identify",
                                      "Inequality perception",
                                      "Merit: Talent",
                                      "Merit: Effort" ),
                custom.gof.names = c("AIC",
                                     "BIC",
                                     "Log Likelihood",
                                     "Num. obs.",
                                     "Num. groups: Individuals",
                                     "Var: Individuals (Intercept)",
                                     "Var: Residual"),
                file = "output/tables/table1-individuales-pond-v2.html")
          #omit.coef = omit

@@

# Hipotesis
h1b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort+merit_effort*ola"
#h2b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort+merit_effort*ola+merit_effort*ola_2"
h6 <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort"

h3b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort+merit_talent*ola"
#h4b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+des_perc*ola+des_perc*ola_2"
#h5b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort+ola_2*pos_id"
#h6b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort+ola_2*sexo"
#h7b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort+ola_2*quintil1"
#h8b <- "ola+ola_2+education+quintil1+ess+edad+sexo+pos_id+des_perc+merit_talent+merit_effort+ola_2*edad"

# A. justification educational inequality
educ1 <- lmer(formula(paste0("just_educ~",h1b,"+(ola+merit_effort|idencuesta)")),data = df_study1, weights = ponderador_long_total)
#educ2 <- lmer(formula(paste0("just_educ~",h2b,"+(ola+ola_2+merit_effort|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ3 <- lmer(formula(paste0("just_educ~",h3b,"+(ola+merit_talent|idencuesta)")),data = df_study1, weights = ponderador_long_total)
educ6 <- lmer(formula(paste0("just_educ~",h6,"+(1|idencuesta)")),data = df_study1, weights = ponderador_long_total)
#educ4 <- lmer(formula(paste0("just_educ~",h4b,"+(ola+ola_2+des_perc|idencuesta)")),data = df_study1, weights = ponderador_long_total)
#educ5 <- lmer(formula(paste0("just_educ~",h5b,"+(ola+ola_2|idencuesta)")),data = df_study1, weights = ponderador_long_total)
#educ6 <- lmer(formula(paste0("just_educ~",h6b,"+(ola+ola_2|idencuesta)")),data = df_study1, weights = ponderador_long_total)
#educ7 <- lmer(formula(paste0("just_educ~",h7b,"+(ola+ola_2|idencuesta)")),data = df_study1, weights = ponderador_long_total)
#educ8 <- lmer(formula(paste0("just_educ~",h8b,"+(ola+ola_2|idencuesta)")),data = df_study1, weights = ponderador_long_total)

# table 3: interacciones
omit <- "(education)|(ess)|(quintil1)|(edad)|(sexo)|(pos_id)|(des_perc)"
texreg::htmlreg(list(educ6,educ3,educ1),
                custom.note = "*** p < 0.001; ** p < 0.01; * p < 0.05. <br>
Note: All the models are controlled by educational level, income quintile, subjective social status, age, gender, <br> political position and inequality perception",
                omit.coef = omit,
                custom.coef.names = c("Intercept",
                                      "Wave",
                                      "Wave^2",
                                      "Merit: Talent",
                                      "Merit: Effort",
                                      "Wave * Merit: Talent",
                                      "Wave * Merit: Effort"
                                      ),
                custom.gof.names = c("AIC", "BIC", "Log Likelihood",
                                     "Num. obs.",
                                     "Num. groups: Individuals",
                                     "Var: Individuals (Intercept)",
                                     "Var: Residual",
                                     "Var: Individuals Wave",
                                     "Var: Individuals Merit: Talent",
                                     "Cov: Individuals (Intercept) Wave",
                                     "Cov: Individuals (Intercept) Merit: Talent",
                                     "Cov: Individuals Wave Merit: Talent",
                                     "Var: Individuals Merit: Effort",
                                     "Cov: Individuals (Intercept) Merit: Effort",
                                     "Cov: Individuals Wave Merit: Effort"),
                file = "output/tables/table3-interac_pond.html")
          #omit.coef = omit
